UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-05 main.tex
:pencil: Update introduction

	% In \gls{ambc} \cite{Liu2013b}, ambient signals (e.g., radio, television, and Wi-Fi) are recycled by interactive nodes to harvest energy and establish connection.

@@

	% ambient signals (e.g., radio, television, and Wi-Fi) are recycled by interactive nodes to harvest energy and establish connection.
	% It not only eliminates the need of power source and carrier emitter, but also avoid the cost of dedicated frequency spectrum.

@@

	% By extending the \gls{sic} scheme to multi-node scenario, \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} where the decoding order depends on backscatter channel strength.

@@

	% Although transmission time and reflection ratio can be designed to boost energy efficiency, it requires frequent feedback to passive nodes and incurs high coordination cost.
	% In \cite{Vougioukas2019}, the nodes control the load-switching speed to shift the scattered signal to desired frequency band, enabling backscatter \gls{fdma}.

@@

	% It requires extra bandwidth and consumes more power at passive nodes.
	% In \cite{Han2021}, random code-assisted backscatter multiple access was introduced to \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.

@@

	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
	% The scattered/reflected signals contain no additional information, but adds constructively (or destructively) with the direct component to enhance desired link (or suppress interference).
	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference, improving spectrum and energy efficiency.
	% Specifically, different IRS reflec- tion coefficients are set for different time slots in each channel coherence block to enable more flexible reflection design with generally less number of users selected to be served at each time slot, thus leading to a higher passive beamforming gain
	% Extensive research has been devoted to optimizing \gls{ris} phase shifts to improve communication, sensing, and power performances.
	Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
	It motivated the use of fixed reflection pattern during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	% To create artificial diversity and enable flexible resource allocation, the concept of dynamic passive beamforming was first proposed for \gls{ofdm} systems \cite{Yang2020},
	% The concept of dynamic passive beamforming that chooses \gls{ris} reflection coefficients independently over different time slots within each channel block was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
	% The concept of dynamic passive beamforming, namely choosing \gls{ris} reflection coefficients independently over different time slots within each channel block, was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients for different time slots within channel block, was first proposed to assist \gls{ofdm} systems \cite{Yang2020}, then extended for the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	Dynamic \gls{ris} introduced artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
	% Interestingly, \cite{Karasik2020} reported from information-theoretic perspective that if
	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary equipment to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
	% From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a pure auxiliary device to maximize the \gls{snr} at the receiver is generally rate-suboptimal for finite input constellations.
	% The capacity-achieving transmission scheme is to joint
	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, while layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
	Further attempts

	How to combine backscatter modulation and passive beamforming

	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{ris}.
	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2020} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
	% The capacity-achieving \gls{ris} strategy was found to
	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.

	% In contrast, dynamic passive beamforming that adjusts \gls{ris} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	% In contrast, dynamic passive beamforming that adjusts \gls{ris} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	Besides, \cite{Yang2020} proposed a dynamic passive beamforming that further adjusts \gls{ris} over fine-grained time slots for \gls{ofdm} systems to balance beamforming gain and multiuser diversity.
	The idea was further applied to \gls{wpcn} to accommodate the downlink \gls{wpt} phase and uplink \gls{wit} phase of the ``harvest-then-transmit'' protocol \cite{Wu2021d,Hua2022a}.
	% For multiuser \gls{wpt}, \cite{Qiu2022} also reported that despite \gls{ris} is restricted to single-beam reflection, dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
	For multiuser \gls{wpt}, \cite{Qiu2022} also reported that dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.
	% However, dynamic passive beamforming demands additional computational complexity and control overhead, and the performance-cost tradeoff needs reconsideration especially when the number of \gls{ris} elements is large.
	% Although dynamic passive beamforming can artificially create time-varying channels for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
	% Although dynamic passive beamforming can artificially introduce temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational complexity and control overhead, and the performance-cost tradeoff deserves further attention.
	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{ris}.
	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2020} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
	% The capacity-achieving \gls{ris} strategy was found to
	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.

>>>>

@@

@@

@@

@@

@@

	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
	Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
	It motivated the use of fixed reflection pattern during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	Dynamic \gls{ris} provided artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary equipment to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} as an information source that combines passive beamforming and backscatter modulation in the overall reflection pattern.
	In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
	However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.

	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
